---
title: "Weighted Cox Model Estimation Methodology"
output: 
  html_document:
         code_folding: hide
         toc: true
         toc_depth: 3
bibliography: ../references.bib
vignette: >
  %\VignetteIndexEntry{Weighted Cox Model Estimation Methodology}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6
)
```

# Overview

This article describes the weighted Cox model estimation methodology implemented in the `weightedsurv` package.  Weighted Cox models extend the standard Cox proportional hazards framework by incorporating time-dependent weight functions into the partial likelihood.  These weights allow the analyst to emphasize treatment effects at different points on the survival distribution --- for example, weighting later time-points more heavily in late-separation scenarios common in immunotherapy trials.

The methodological foundations draw on the work of @Lin1991 and @Sasieni1993 who developed the theory for weighted partial-likelihood estimation, and @LLA2020 who proposed companion weighted Cox estimators linked to weighted log-rank combination tests.

The `weightedsurv` package provides a unified interface for computing weighted Cox model estimates across multiple weighting schemes, with variance estimation based on both asymptotic and synthetic-martingale resampling approaches.


# Background: Non-Proportional Hazards and the Standard Cox Model

## The Two-Sample Setting

Consider the standard two-sample random censorship model used in clinical trials.  For $i = 1, \ldots, n$ let $Z_i = j$ if observation $i$ is from group $j \in \{0, 1\}$ with $n = n_0 + n_1$.  Let $T$ denote the survival time and $C$ the censoring time.  We observe $X = \min(T, C)$ and $\Delta = I(T \le C)$.  Survival times are assumed independent of censoring conditional on treatment.

The at-risk and counting processes are
$$Y_i(t) = I(X_i \ge t), \quad N_i(t) = I(X_i \le t,\, \Delta_i = 1).$$

The standard Cox model assumes $\lambda(t \mid Z) = \lambda_0(t) \exp(\beta Z)$, yielding a constant hazard ratio $\exp(\beta)$.  The maximum partial-likelihood estimator $\hat{\beta}$ solves the score equation

$$U(\beta) = \sum_{i=1}^{n} \int_0^\infty \left\{ Z_i - \frac{S^{(1)}(t, \beta)}{S^{(0)}(t, \beta)} \right\} dN_i(t) = 0,$$

where $S^{(p)}(t, \beta) = n^{-1} \sum_{i=1}^{n} Z_i^p\, Y_i(t)\, \exp(Z_i \beta)$ for $p = 0, 1$.

## Why Weighted Cox Models?

Under non-proportional hazards the true model is $\lambda(t \mid Z) = \lambda_0(t) \exp(\beta(t) Z)$ with a time-varying coefficient $\beta(t)$.  In this case the standard Cox estimator converges to a weighted average of $\beta(t)$ that depends on the censoring distribution, risk-set composition, and the pattern of non-proportional hazards.  The resulting "average hazard ratio" may not accurately reflect the treatment effect at clinically relevant time periods.

For example, in a late-separation scenario where $\beta(t) = 0$ for $t \le \tau_{cp}$ and $\beta(t) = \log(\theta)$ for $t > \tau_{cp}$, the standard Cox estimator attenuates the true later-term effect toward the null because it gives substantial weight to the early period where there is no treatment difference.

Weighted Cox models address this by introducing a time-dependent weight function $w(t)$ into the partial likelihood, allowing the analyst to emphasize contributions from specific time regions.


# Weighted Partial Likelihood

## Definition

The $w$-weighted partial likelihood is

$$\ell_w(\beta) = \sum_{i=1}^{n} \int_0^\infty w(t)\, \beta\, Z_i\, dN_i(t) - \int_0^\infty w(t) \log\!\bigl(S^{(0)}(t, \beta)\bigr) \sum_{i=1}^{n} dN_i(t),$$

where $w(t) \ge 0$ is a predictable weight function.  The weighted Cox estimator $\hat{\beta}_w$ maximizes $\ell_w(\beta)$ and solves

$$U_w(\beta) = \sum_{i=1}^{n} \int_0^\infty w(t) \left\{ Z_i - \frac{S^{(1)}(t, \beta)}{S^{(0)}(t, \beta)} \right\} dN_i(t) = 0.$$

Note that for $w(t) \equiv 1$ this reduces to the standard Cox score equation, and in the two-sample setting $U_w(0)$ evaluated at $\beta = 0$ is the weighted log-rank statistic.

## Weighting Schemes and Their Rationale

The `weightedsurv` package implements several weighting schemes through the `wt.rg.S()` function and the `cox_rhogamma()` interface.  Each scheme corresponds to a different emphasis on the survival time scale:

**Fleming-Harrington FH($\rho$, $\gamma$):** The weight function is
$$w(t) = \bigl[\hat{\bar{F}}(t^-)\bigr]^\rho \bigl[1 - \hat{\bar{F}}(t^-)\bigr]^\gamma,$$
where $\hat{\bar{F}}(t^-)$ is the left-continuous pooled Kaplan-Meier estimator and $\rho \ge 0$, $\gamma \ge 0$.  The standard log-rank / Cox model corresponds to FH(0, 0).  Increasing $\gamma$ (with $\rho = 0$) emphasizes late differences; increasing $\rho$ (with $\gamma = 0$) emphasizes early differences.

**Magirr-Burman (MB):**
$$w(t) = \frac{1}{\max\bigl(\hat{\bar{F}}(t^-),\, \hat{\bar{F}}(t^\star)\bigr)},$$
which provides modest downweighting of early time-points relative to the user-specified cutoff $t^\star$.

**Schemper:**
$$w(t) = \frac{\hat{\bar{F}}(t^-)}{\hat{\bar{G}}(t)},$$
where $\hat{\bar{G}}$ is the pooled Kaplan-Meier censoring survivor function.  This scheme produces an "average hazard ratio" estimator that is approximately free of the censoring distribution.

**Xu-O'Quigley (XO):**
$$w(t) = \frac{\hat{\bar{F}}(t^-)}{\bar{Y}(t)/n},$$
which also yields a censoring-independent average hazard ratio estimator.

**Custom time-based:** Step-function weights of the form $w(t) = w_0\, I(t \le \tau) + w_1\, I(t > \tau)$, which allow the analyst to zero-out contributions before or after a pre-specified time-point.


## Variance Estimation

The variance of $\hat{\beta}_w$ is estimated through the weighted observed information and weighted score variance.  The weighted information is

$$I_w(\beta) = \int_0^\infty w(t) \left\{ \frac{\bar{Y}_0(t)\, \exp(\beta)\, \bar{Y}_1(t)}{\bigl(\bar{Y}_0(t) + \exp(\beta)\, \bar{Y}_1(t)\bigr)^2} \right\} d\bar{N}(t),$$

and the score variance $\hat{\sigma}^2(U_w(\beta))$ is estimated (evaluated at $\hat{\beta}_w$) following the martingale-based approach of @FH1991:

$$\hat{\sigma}^2(U_w(\beta)) = \int_0^\infty \left\{ \frac{K(t, \beta)^2}{\bar{Y}_0(t)} + \frac{K(t, \beta)^2}{\exp(\beta)\, \bar{Y}_1(t)} \right\} \left\{1 - \frac{\Delta\bar{N}(t) - 1}{\bar{Y}_0(t) + \exp(\beta)\bar{Y}_1(t) - 1} \right\} \frac{d\bar{N}(t)}{\bar{Y}_0(t) + \exp(\beta)\bar{Y}_1(t)},$$

where $K(t, \beta)$ is the FH weight kernel evaluated at $\beta$.  Note that at $\beta = 0$ the score statistic and its variance reduce to the weighted log-rank statistic and its standard variance estimator.

The standard error of $\hat{\beta}_w$ is then $\hat{\sigma}_w = \hat{\sigma}(U_w(\hat{\beta}_w)) / I_w(\hat{\beta}_w)$.


## Synthetic-Martingale Resampling

In addition to asymptotic standard errors, `weightedsurv` implements synthetic-martingale resampling for variance estimation, which can have improved small-sample properties.  The idea (@DBP2017) is to replace the unobservable martingale increments $dM_{i,j}$ with independent standard normal realizations multiplied by observable counting-process increments:

$$U_w^\dagger(\hat{\beta}_w) = \sum_{i=1}^{n} \int_0^\infty w(t) \left\{ Z_i - \frac{S^{(1)}(t, \hat{\beta}_w)}{S^{(0)}(t, \hat{\beta}_w)} \right\} dG_i\, N_i(t),$$

where $G_i \stackrel{\text{iid}}{\sim} N(0, 1)$ are independent of the data.  The resampled distribution of $I_w(\hat{\beta}_w)^{-1} U_w^\dagger(\hat{\beta}_w)$ approximates the sampling distribution of $\hat{\beta}_w - \beta_w^*$.  Repeating this process a large number of times (`draws` in `cox_rhogamma()`) yields resampling-based confidence intervals.

This approach extends naturally to constructing **simultaneous confidence intervals** across multiple weighting schemes, which is critical when the weighting scheme is selected via a combination test (see @LLA2020).


# Asymptotic Properties Under Misspecification

## The Estimand: What Does $\hat{\beta}_w$ Estimate?

Under regularity conditions (@Lin1991), $\hat{\beta}_w$ converges in probability to $\beta_w^*$, the solution to $u_w(\beta) = 0$ where

$$u_w(\beta) = \int_0^\infty w^\dagger(t) \left\{ \frac{s^{(1)}(t)}{s^{(0)}(t)} - \frac{s^{(1)}(t, \beta)}{s^{(0)}(t, \beta)} \right\} s^{(0)}(t)\, dt,$$

with $w^\dagger(t)$ the probability limit of $w(t)$, and $s^{(p)}(t) = E[S^{(p)}(t)]$, $s^{(p)}(t, \beta) = E[S^{(p)}(t, \beta)]$.

This shows that $\beta_w^*$ is a weighted average (on the log-hazard scale) of the time-varying $\beta(t)$, with weights determined jointly by $w(t)$, the censoring distribution, and the risk-set dynamics.

## Late-Separation Scenario

To build intuition, consider the change-point model $\beta(t) = \log(\theta)\, I(t > \tau_{cp})$ with equal randomization ($\Pr(Z = 1) = 1/2$) and censoring independent of treatment.  Then $\beta_w^*$ satisfies

$$0 = \int_0^{\tau_{cp}} w^\dagger(t) \left\{ \frac{1}{2} - \frac{\exp(\beta_w^*)}{1 + \exp(\beta_w^*)} \right\} \lambda_0(t)\, \bar{G}(t)\, \bar{F}_0(t)\, dt + \int_{\tau_{cp}}^\infty w^\dagger(t) \left\{ \exp(\beta_w^*)\, a(t, \beta_w^*) - \theta \right\} \tfrac{1}{2}\, \lambda_0(t)\, \bar{G}(t)\, \bar{F}_1(t)\, dt,$$

where $a(t, \beta_w^*) = [\bar{F}_1(t)\, \theta + \bar{F}_0(t)] / [\bar{F}_1(t)\, \exp(\beta_w^*) + \bar{F}_0(t)]$.

The first integral covers the null period ($t \le \tau_{cp}$) where the contribution pushes $\beta_w^*$ toward zero; the second integral covers the treatment-effect period ($t > \tau_{cp}$) and pushes $\beta_w^*$ toward $\log(\theta)$.  Weighting schemes that downweight the first integral (e.g., FH(0,1)) therefore produce estimands closer to the true treatment effect $\theta$.


# Using `weightedsurv` for Weighted Cox Estimation

## Workflow

The typical workflow for weighted Cox estimation in `weightedsurv` involves:

1. Prepare a counting-process dataset via `df_counting()` or `get_dfcounting()`
2. Fit weighted Cox models via `cox_rhogamma()` with the desired weighting scheme
3. Optionally, use resampling (the `draws` argument) for improved inference

The `df_counting()` function computes risk sets, event counts, Kaplan-Meier estimates, and the specified weighting scheme.  The `cox_rhogamma()` function then uses this counting-process representation to solve the weighted score equation.


## Example: GBSG Trial Data

We illustrate using the GBSG randomized trial data available in the `survival` package.

```{r data-prep}
library(survival)
library(weightedsurv)
library(data.table)

# Prepare GBSG data
df_gbsg <- gbsg
df_gbsg$tte <- df_gbsg$rfstime / 30.4375  # Convert days to months
df_gbsg$event <- df_gbsg$status
df_gbsg$treat <- df_gbsg$hormon

tte.name <- "tte"
event.name <- "event"
treat.name <- "treat"
arms <- c("treat", "control")
```

### Step 1: Counting-Process Dataset

The `df_counting()` function computes the full counting-process representation along with the specified weighting scheme:

```{r dfcount}
# Standard (unweighted) analysis with FH(0,0) = standard log-rank / Cox
dfcount_gbsg <- df_counting(
  df = df_gbsg, 
  tte.name = tte.name, 
  event.name = event.name, 
  treat.name = treat.name, 
  arms = arms,
  by.risk = 12, 
  scheme = "fh", 
  scheme_params = list(rho = 0, gamma = 0)
)
```

### Step 2: Standard Cox Model

With FH(0,0) weights the weighted Cox model reduces to the standard Cox model:

```{r cox-standard}
# Standard Cox via cox_rhogamma with FH(0,0)
fit_cox <- cox_rhogamma(
  dfcount = dfcount_gbsg, 
  scheme = "fh", 
  scheme_params = list(rho = 0, gamma = 0), 
  draws = 1000, 
  verbose = FALSE
)

cat("Standard Cox model\n")
cat("  HR:", round(fit_cox$hr_ci_asy$hr, 3), "\n")
cat("  95% CI (asymptotic):", 
    round(fit_cox$hr_ci_asy$lower, 3), "-", 
    round(fit_cox$hr_ci_asy$upper, 3), "\n")
cat("  95% CI (resampling):", 
    round(fit_cox$hr_ci_star$lower, 3), "-", 
    round(fit_cox$hr_ci_star$upper, 3), "\n")
cat("  Z-score:", round(fit_cox$z.score, 3), "\n")
```

### Step 3: Weighted Cox Models with Different Schemes

Now we fit weighted Cox models with several weighting schemes to examine how emphasis on different time regions affects the hazard ratio estimate:

```{r cox-weighted}
# FH(0,1): Late-emphasis weighting
fit_fh01 <- cox_rhogamma(
  dfcount = dfcount_gbsg, 
  scheme = "fh", 
  scheme_params = list(rho = 0, gamma = 1), 
  draws = 1000, 
  verbose = FALSE
)

# FH(1,0): Early-emphasis weighting
fit_fh10 <- cox_rhogamma(
  dfcount = dfcount_gbsg, 
  scheme = "fh", 
  scheme_params = list(rho = 1, gamma = 0), 
  draws = 1000, 
  verbose = FALSE
)

# Magirr-Burman with 12-month cutoff
fit_mb <- cox_rhogamma(
  dfcount = dfcount_gbsg, 
  scheme = "MB", 
  scheme_params = list(mb_tstar = 12), 
  draws = 1000, 
  verbose = FALSE
)

# Custom: Zero weight before 6 months, unit weight after
fit_custom <- cox_rhogamma(
  dfcount = dfcount_gbsg, 
  scheme = "custom_time", 
  scheme_params = list(t.tau = 6, w0.tau = 0, w1.tau = 1), 
  draws = 1000, 
  verbose = FALSE
)
```

### Comparison of Results

```{r results-table}
library(gt)

results <- data.table(
  Scheme = c("FH(0,0) [Standard Cox]", "FH(0,1) [Late emphasis]", 
             "FH(1,0) [Early emphasis]", "MB(12)", "Custom 0/1 at 6 months"),
  HR = c(fit_cox$hr_ci_asy$hr, fit_fh01$hr_ci_asy$hr, 
         fit_fh10$hr_ci_asy$hr, fit_mb$hr_ci_asy$hr, fit_custom$hr_ci_asy$hr),
  Z = c(fit_cox$z.score, fit_fh01$z.score, 
        fit_fh10$z.score, fit_mb$z.score, fit_custom$z.score),
  Lower = c(fit_cox$hr_ci_star$lower, fit_fh01$hr_ci_star$lower,
            fit_fh10$hr_ci_star$lower, fit_mb$hr_ci_star$lower, fit_custom$hr_ci_star$lower),
  Upper = c(fit_cox$hr_ci_star$upper, fit_fh01$hr_ci_star$upper,
            fit_fh10$hr_ci_star$upper, fit_mb$hr_ci_star$upper, fit_custom$hr_ci_star$upper)
)

results %>% 
  gt() %>% 
  fmt_number(columns = c(HR, Z, Lower, Upper), decimals = 3) %>%
  cols_label(
    Scheme = "Weighting Scheme",
    HR = "Hazard Ratio",
    Z = "Z-score",
    Lower = "95% CI Lower",
    Upper = "95% CI Upper"
  ) %>%
  tab_header(
    title = "Weighted Cox Model Estimates: GBSG Trial",
    subtitle = "Resampling-based 95% confidence intervals (1000 draws)"
  ) %>%
  tab_footnote(
    footnote = "FH(rho, gamma) = Fleming-Harrington weights; MB = Magirr-Burman.",
    locations = cells_column_labels(columns = Scheme)
  )
```

## Visualizing Weight Functions

The `plot_weight_schemes()` function displays the weight profiles over the event time-scale, illustrating how different schemes emphasize different regions:

```{r weight-plot, fig.width = 10, fig.height = 6}
g <- plot_weight_schemes(dfcount_gbsg)
print(g)
```


## Weighted Cox with Propensity-Score Adjustment

The `weightedsurv` package supports subject-specific (case) weights in combination with time-dependent weighting.  This is particularly useful for observational studies where propensity-score weighting is used to adjust for confounding.

```{r rotterdam-ps, fig.width = 10, fig.height = 6}
# Prepare Rotterdam data (observational study)
gbsg_validate <- within(rotterdam, {
  rfstime <- ifelse(recur == 1, rtime, dtime)
  time_months <- rfstime / 30.4375
  status2 <- ifelse(recur == 1 | (recur == 0 & death == 1 & rtime < dtime), recur, death)
  grade3 <- ifelse(grade == "3", 1, 0)
  treat <- hormon
  event <- status2
  tte <- time_months
})
df_rotterdam <- subset(gbsg_validate, nodes > 0)

# Propensity score model
fit.ps <- glm(treat ~ age + meno + size + grade3 + nodes + pgr + chemo + er, 
              data = df_rotterdam, family = "binomial")
pihat <- fit.ps$fitted
pihat.null <- glm(treat ~ 1, family = "binomial", data = df_rotterdam)$fitted
wt.1 <- pihat.null / pihat
wt.0 <- (1 - pihat.null) / (1 - pihat)
df_rotterdam$sw.weights <- ifelse(df_rotterdam$treat == 1, wt.1, wt.0)

# Weighted counting-process dataset (propensity-score weighted)
dfcount_wtd <- get_dfcounting(
  df = df_rotterdam, 
  tte.name = "tte", event.name = "event", treat.name = "treat", 
  arms = arms, by.risk = 24, weight.name = "sw.weights"
)

# Weighted Cox models with propensity-score adjustment
fit_ps_cox <- cox_rhogamma(dfcount = dfcount_wtd, scheme = "fh", 
                            scheme_params = list(rho = 0, gamma = 0), 
                            draws = 1000, verbose = FALSE)

fit_ps_fh01 <- cox_rhogamma(dfcount = dfcount_wtd, scheme = "fh", 
                              scheme_params = list(rho = 0, gamma = 1), 
                              draws = 1000, verbose = FALSE)

cat("Rotterdam propensity-score weighted analyses:\n")
cat("  Standard Cox HR:", round(fit_ps_cox$hr_ci_asy$hr, 3), 
    " 95% CI:", round(fit_ps_cox$hr_ci_star$lower, 3), "-", 
    round(fit_ps_cox$hr_ci_star$upper, 3), "\n")
cat("  FH(0,1) Cox HR:", round(fit_ps_fh01$hr_ci_asy$hr, 3), 
    " 95% CI:", round(fit_ps_fh01$hr_ci_star$lower, 3), "-", 
    round(fit_ps_fh01$hr_ci_star$upper, 3), "\n")
```


# Connection to Weighted Log-Rank Tests

## Score-Test Equivalence

The weighted Cox score statistic evaluated at $\beta = 0$ is algebraically equivalent to the weighted log-rank statistic.  That is, $U_w(0) = W_K$ where

$$W_K = \int_0^\infty \left\{ \frac{K(t)}{\bar{Y}_0(t)}\, d\bar{N}_0(t) - \frac{K(t)}{\bar{Y}_1(t)}\, d\bar{N}_1(t) \right\},$$

with $K(t) = \sqrt{\frac{n_0 + n_1}{n_0\, n_1}}\, w(t) \frac{\bar{Y}_0(t)\, \bar{Y}_1(t)}{\bar{Y}(t)}$.  

This duality connects hypothesis testing (via the weighted log-rank test) and estimation (via the weighted Cox model) under the same weighting scheme, and justifies referring to the weighted Cox estimator as the "companion" to the weighted log-rank test.  In `weightedsurv`, the `check_results()` function verifies this equivalence numerically.

## Companion Estimators and Combination Tests

When multiple weighted log-rank tests are combined in a max-combo test $Z_{\max} = \max(Z_1, \ldots, Z_q)$ (@LLA2020), the "companion" Cox estimator $\hat{\beta}_{\max}$ is the weighted Cox estimate corresponding to the weighting scheme that yielded the largest test statistic.  Since $\hat{\beta}_{\max}$ is selected via a data-dependent process, valid inference requires simultaneous confidence intervals that hold across all $q$ weighting schemes.

The critical value $c_{\max}$ is determined such that

$$\Pr\!\left\{\max\!\left(\left|\frac{\hat{\beta}_{w_1}}{\hat{\sigma}_{w_1}}\right|, \ldots, \left|\frac{\hat{\beta}_{w_q}}{\hat{\sigma}_{w_q}}\right|\right) \le c_{\max}\right\} \approx 1 - \alpha,$$

which is computed via the same synthetic-martingale resampling using common $G_i$ draws across all $q$ weighting schemes, thereby preserving the correlation structure.


# Interpretation and Estimands

## What Does the Weighted Hazard Ratio Mean?

Under non-proportional hazards each weighted Cox estimator converges to a different estimand $\exp(\beta_w^*)$ that reflects the weighting-specific average of the time-varying hazard ratio.  The following interpretive principles apply:

- **FH(0,0)** (standard Cox): Estimates an overall average hazard ratio.  Under proportional hazards it estimates the true constant HR.
- **FH(0, $\gamma$) with $\gamma > 0$** (late emphasis): Estimates a hazard ratio that more heavily reflects later-term treatment effects.  Under late-separation, this is closer to the true treatment benefit after the change-point.
- **FH($\rho$, 0) with $\rho > 0$** (early emphasis): Estimates a hazard ratio reflecting early treatment effects.  Under early-separation, this captures the initial treatment benefit.
- **Schemper / XO**: Estimate "average hazard ratios" that are approximately independent of the censoring distribution.

## Censoring Dependence

In general, the estimand $\beta_w^*$ depends on the censoring distribution through its influence on the risk-set dynamics and the probability limit of the weights.  The Schemper and XO weighting schemes were specifically designed to yield estimands that are (asymptotically) free of the censoring distribution $G$.  For FH weights, the degree of censoring dependence can be evaluated numerically using the limiting equation described above.

## Cautions

As discussed by @Hernan2010, @ACR2015, and @SRR2019, hazard ratios --- even under randomization and ideal proportional hazards conditions --- are subject to potential selection bias through temporal conditioning on risk sets.  Weighted Cox estimators may further complicate these dynamics through the additional time-dependent weighting.  The weighted hazard ratio should therefore be interpreted as a complementary summary of treatment effect with careful attention to what the specific weighting pattern emphasizes.


# Summary

The weighted Cox model estimation framework in `weightedsurv` provides:

- **Flexible weighting** via multiple schemes (FH, MB, Schemper, XO, custom) through a unified `cox_rhogamma()` interface
- **Dual inference**: Both asymptotic and resampling-based standard errors and confidence intervals
- **Score-test duality**: Direct connection between weighted Cox estimation and weighted log-rank testing
- **Propensity-score compatibility**: Subject-specific case weights can be combined with time-dependent weighting
- **Simultaneous inference**: Support for simultaneous confidence intervals needed when the weighting scheme is selected via a combination test

The key functions are:

| Function | Role |
|----------|------|
| `df_counting()` / `get_dfcounting()` | Prepare counting-process data with weights |
| `cox_rhogamma()` | Fit weighted Cox models with asymptotic and resampling inference |
| `wt.rg.S()` | Compute time-dependent weight functions |
| `plot_weight_schemes()` | Visualize weight profiles |
| `check_results()` | Verify score-test equivalence |
| `wlr_dhat_estimates()` | Weighted log-rank with survival-difference estimates |


# References
